\textbf{\glsfmtfull{ris}:\\Beamforming, Modulation, and Channel Shaping}

### 2024-05-02 viva/slides_lite.tex
:sparkles: Add lite slides

	\begin{frame}{Ancestor of \glsfmtshort{ris}: Reflectarray antenna}
		% not parabolic with parallel phase front
		A reflectarray antenna consists of an array illuminated by a feeding antenna \cite{Deng2016}.
		\begin{figure}
			\centering
			\includegraphics[width=0.45\textwidth]{../assets/viva/reflectarray.png}
		\end{figure}
		A progressive phase shift can be applied to the unit cells (a.k.a. elements) to steer the beam direction.
	\end{frame}

	\begin{frame}{What is the difference in \glsfmtshort{ris}?}
		\begin{enumerate}
			\item Metamaterial enables \textcolor{blue}{real-time control} and \textcolor{blue}{unconventional bahavior}.
			\item Impinging waves can be \textcolor{blue}{partially refracted and reflected}.
			\item The feed can be \textcolor{blue}{mobile} while the surface is \textcolor{blue}{scalable and multi-functional}.
			\item Elements can be physically interconnected for \textcolor{blue}{cooperative wave scattering}.
		\end{enumerate}
		\begin{exampleblock}{Refraction}
			\begin{columns}[T]
				\begin{column}{.25\textwidth}
					\begin{figure}
						\centering
						\resizebox{\columnwidth}{!}{
							\input{../assets/viva/nim_focus.tex}
						}
					\end{figure}
				\end{column}
				% \hfill
				\begin{column}{.6\textwidth}
					\vspace{0.5cm}
					\begin{itemize}
						\item Negative index material can focus waves
						\item Amplitude and phase responses can be tuned by diodes and \glsfmtshort{fpga}
						\item Similar for wave reflection
					\end{itemize}
				\end{column}
			\end{columns}
		\end{exampleblock}
		\begin{exampleblock}{Reflection}
			\vspace{-1cm}
			\begin{figure}[H]
				\centering
				\subfloat[Incident wave\label{fg:wave_incident}]{
					\resizebox{!}{2.02cm}{
						\input{../assets/viva/wave_incident.tex}
					}
				}
				\subfloat[Reflected wave\label{fg:wave_reflected}]{
					\resizebox{!}{2cm}{
						\input{../assets/viva/wave_reflected.tex}
					}
				}
			\end{figure}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Use case: Beamforming}
		% \textcolor{blue}{Joint beamforming} design of \gls{ris} and transceiver for a specific performance measure \cite{Wu2020}.
		% \gls{ris} and transceiver \textcolor{blue}{joint beamforming} design for a specific performance measure \cite{Wu2020}.
		\textcolor{blue}{Beamforming} of \gls{ris} and transceiver can be jointly designed for a specific performance measure \cite{Wu2020}.
		\begin{figure}
			\centering
			\subfloat[Coverage extension]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_coverage.jpg}
				}
			}
			\subfloat[Security enhancement]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_security.jpg}
				}
			}
			\subfloat[Interference mitigation]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_interference.jpg}
				}
			}
			\\
			\subfloat[Assist \glsfmtshort{d2d} network]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_network.jpg}
				}
			}
			\subfloat[Assist information and power transfer]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_swipt.jpg}
				}
			}
		\end{figure}
	\end{frame}

	\begin{frame}{Use case: Modulation}
		\gls{ris} can be used for backscatter \textcolor{blue}{modulation} by periodically switching the reflection pattern \cite{Hu2021a}.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{../assets/viva/ris_modulation.pdf}
		\end{figure}
	\end{frame}

	\begin{frame}{Use case: Channel shaping}
		\textcolor{blue}{Channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment \cite{Arslan2022}.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{../assets/viva/ris_shaping.pdf}
		\end{figure}
	\end{frame}
\end{section}

@@

	\begin{frame}{\glsfmtshort{wpt} via radio waves}
		\vspace{-0.5cm}
		\begin{table}
			\footnotesize
			\rowcolors{2}{gray!25}{white}
			\renewcommand{\arraystretch}{1.25}
			\resizebox{\linewidth}{!}{
				\begin{tabular}{c c c c c c}
					\toprule
					% \hiderowcolors
					Categories                   & Medium                     & Device                     & Power level                            & Frequency                                & Range                     \\ \midrule
					% \showrowcolors
					                             & Magnetic resonant coupling & Resonators                 & Up to \SI{10}{\W}                      & \si{\kHz} -- \si{\MHz}                   & \si{\m}                   \\
					\cellcolor{white}            & Inductive coupling         & Wire coils                 & Up to \SI{10}{\W}                      & \si{\Hz} -- \si{\MHz}                    & \si{\cm}                  \\
					\multirow{-3}{*}{Near-field} & Capacitive coupling        & Metal plates               & Up to \SI{1}{\W}                       & \si{\kHz} -- \si{\MHz}                   & \si{\mm}                  \\
					\cellcolor{white}            & \textcolor{blue}{\gls{rf} wave}  & \textcolor{blue}{Rectenna} & \textcolor{blue}{\si{\uW} -- \si{\mW}} & \textcolor{blue}{\si{\MHz} -- \si{\GHz}} & \textcolor{blue}{\si{\m}} \\
					\multirow{-2}{*}{Far-field}  & Light wave                 & Laser                      & \si{\uW} -- \si{\mW}                   & \si{\THz}                                & \si{\km}                  \\ \bottomrule
				\end{tabular}
			}
		\end{table}
		\vspace{-0.25cm}
		\begin{figure}[H]
			\centering
			\resizebox{\columnwidth}{!}{
				\input{../assets/viva/wpt_architecture.tex}
			}
			\label{fg:wpt_architecture}
		\end{figure}
		\vspace{-1em}
		The end-to-end \gls{wpt} efficiency is
		\begin{equation*}
			\eta = \frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{T}} = \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{T}}{P_{\mathrm{DC}}^\mathrm{T}}}_{\eta_1} \textcolor{orange}{\underbrace{\frac{P_{\mathrm{RF}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{T}}}_{\eta_2}} \textcolor{blue}{\underbrace{\frac{P_{\mathrm{DC}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{R}}}_{\eta_3}} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{R}}}_{\eta_4}
		\end{equation*}
		where $\eta_2$ and $\eta_3$ models the channel and rectenna, respectively.
	\end{frame}

	\begin{frame}{Received signal and harvested power}
		The rectenna efficiency $\eta_3$ depends on its input waveform (power and shape).
		\begin{block}{Rectenna model}
			% \vspace{-0.25cm}
			% \begin{figure}[H]
			% 	\centering
			% 	\subfloat[Rectenna]{
			% 		\resizebox{0.35\columnwidth}{!}{
			% 			\input{../assets/viva/rectenna.tex}
			% 		}
			% 		\label{fg:rectenna}
			% 	}
			% 	\subfloat[Half-wave rectifier]{
			% 		\resizebox{0.35\columnwidth}{!}{
			% 			\input{../assets/viva/halfwave_rectifier.tex}
			% 		}
			% 		\label{fg:halfwave_rectifier}
			% 	}
			% \end{figure}
			% \vspace{-0.25cm}
			\begin{itemize}
				\item Linear region (constant $\eta_3$): $P_{\mathrm{DC}}^\mathrm{R} = \eta_3 P_\mathrm{RF}^\mathrm{R} = \eta_3 \mathbb{A}\bigl\{ \lvert y(t) \rvert^2 \bigr\}$
				\item Non-linear region: Taylor expansion on diode characteristic equation
				\vspace{-0.25cm}
				\begin{equation*}
					\arg_{x(t)} \max P_{\mathrm{DC}}^\mathrm{R} = \arg_{x(t)} \max z \triangleq \sum_{i=2,\text{even}}^{n_0} \beta_i \mathbb{A}\bigl\{ y^i(t) \bigr\},
					\vspace{-0.5cm}
				\end{equation*}
				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant and $n_0$ is the truncation order.
			\end{itemize}
		\end{block}
		\begin{alertblock}{In multi-carrier \glsfmtshort{wpt} \textellipsis}
			\begin{itemize}
				\item $n_0 \ge 4$ allows components to compensate each other for higher \gls{dc} power
				\item High \gls{papr} (e.g., multi-sine) is preferred \cite{Trotter2009}
			\end{itemize}
			\vspace{-0.5cm}
			\begin{figure}
				\centering
				\subfloat{
					\resizebox{!}{2.5cm}{
						\includegraphics{../assets/viva/multisine_frequency_domain.eps}
					}
				}
				\subfloat{
					\resizebox{!}{2.5cm}{
						\includegraphics{../assets/viva/multisine_time_domain.eps}
					}
				}
			\end{figure}
		\end{alertblock}
	\end{frame}

	\begin{frame}{From \glsfmtshort{wpt} to \gls{ris}-aided \glsfmtshort{swipt}}
		\begin{figure}[H]
			\centering
			\def\svgwidth{0.5\columnwidth}
			\input{../assets/viva/system.eps_tex}
		\end{figure}

		\begin{itemize}
			\item \gls{swipt} features shared signal, spectrum, and infrastructure
			\item \gls{ris} enhances the RF-to-RF efficiency $\eta_2$ which has been a major concern
		\end{itemize}
		\begin{block}{Transmit waveform}
			\begin{equation*}
				\mathbf{x}(t) = \Re \left\{\sum_{n=1}^N \Bigl(\mathbf{w}_{\mathrm{I},n} \cdot \underbrace{\tilde{x}_{\mathrm{I},n}(t) e^{\jmath 2{\pi}{f_n}{t}}}_\text{modulated}+\mathbf{w}_{\mathrm{P},n} \cdot \underbrace{e^{\jmath 2{\pi}{f_n}{t}}}_\text{multi-sine}\Bigr) \right\}
			\end{equation*}
		\end{block}
		\begin{block}{Frequency-flat \glsfmtshort{ris} model}
			\begin{equation*}
				\mathbf{h}_{n}^\mathsf{H} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{h}_{\mathrm{B},n}^\mathsf{H} \mathbf{\Theta} \mathbf{H}_{\mathrm{F},n}
			\end{equation*}
		\end{block}
	\end{frame}

	\begin{frame}{Performance analysis}
		\begin{block}{Receiver architectures}
			\vspace{-0.5cm}
			\begin{figure}
				\centering
				\subfloat[\gls{ts} receiver]{
					\resizebox{0.48\columnwidth}{!}{
						\input{../assets/viva/receiver_ts.tex}
					}
					\label{fg:receiver_ts}
				}
				\subfloat[\gls{ps} receiver]{
					\resizebox{0.48\columnwidth}{!}{
						\input{../assets/viva/receiver_ps.tex}
					}
					\label{fg:receiver_ps}
				}
			\end{figure}
		\end{block}
		\begin{block}{\glsfmtfull{r-e} region of \glsfmtshort{ps}}
			\vspace{-0.25cm}
			\begin{align*}
				R(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\rho) &= \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},\\
				z(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho) &= \sum_{i=2,\text{even}}^{n_0}{\beta_i}{\rho^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y^i(t)\right\}\right\}},
			\end{align*}
			\begin{equation*}
				\mathcal{C}_\mathrm{R-E}(P)\triangleq \Bigl\{(r,e) : 0 \le r \le R, \ 0 \le e \le z, \lVert{\mathbf{W}_{\mathrm{I}}}\rVert _\mathrm{F}^2/2 + \lVert{\mathbf{W}_{\mathrm{P}}}\rVert _\mathrm{F}^2/2 \le P \Bigr\}
			\end{equation*}
		\end{block}
	\end{frame}

@@

	\begin{frame}{Simulation results: Number of subbands $N$}
		\begin{figure}
			\centering
			\subfloat[\gls{r-e} region]{
				\resizebox{0.45\columnwidth}{!}{
					\input{../assets/viva/re_subband.tex}
				}
			}
			\subfloat[Waveform amplitude]{
				\resizebox{0.45\columnwidth}{!}{
					\input{../assets/viva/waveform_subband.tex}
				}
			}
		\end{figure}
		\begin{itemize}
			\item Increasing $N$ reduces per-subband rate but boosts harvested energy
			\item Region is convex at small $N$ (favors \gls{ps}) and concave at large $N$ (favors \gls{ts})
			\item Dedicated multi-sine power waveform is unnecessary at small $N$
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Node architecture}
		\vspace{-0.5cm}
		\begin{figure}
			\centering
			\subfloat[Block Diagram]{
				\resizebox{!}{2cm}{
					\input{../assets/viva/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[\glsentryshort{rfid} tag with harvester \cite{Molina-Farrugia2017}]{
				\resizebox{!}{2.5cm}{
					\includegraphics[width=0.9\linewidth]{../assets/viva/passive_tag_prototype.png}
				}
				\label{fi:passive_tag_prototype}
			}\\
			\subfloat[Equivalent Circuit]{
				\resizebox{0.7\linewidth}{!}{
					\input{../assets/viva/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
		\end{figure}
		Impinging waves can be used for powering, modulation, \textcolor{blue}{and beamforming.}
	\end{frame}

	\begin{frame}{Reflection coefficient}
		The node changes state by switching load impedance (and reflection coefficient)
		\begin{equation*}
			\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0}
		\end{equation*}
		\vspace{-0.25cm}
		\begin{figure}
			\centering
			\resizebox{0.6\columnwidth}{!}{
				\input{../assets/viva/time_structure.tex}
			}
		\end{figure}
		\vspace{-0.25cm}
		\begin{itemize}
			\item \gls{ris}: the state at a specific time is known (as a passive beamforming codeword) to the transceiver
			\begin{equation*}
				\Gamma_m = \exp(j \phi_m),
			\end{equation*}
			\item \gls{bc}: all states occur with equal probability (as part of information codeword) to be detected at the receiver
			\begin{equation*}
				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\end{equation*}
		\end{itemize}
	\end{frame}

	\begin{frame}{RIScatter system}
		\begin{table}
			\rowcolors{2}{gray!25}{white}
			\renewcommand{\arraystretch}{1.25}
			\resizebox{\linewidth}{!}{
				\begin{tabular}{c c c c c c}
					\toprule
					\hiderowcolors
					                       & Backscatter        & Ambient backscatter         & Symbiotic radio          & \gls{ris}           & RIScatter                        \\ \midrule
					\showrowcolors
					Information link(s)    & Backscatter        & Coexisting                  & Coexisting               & Primary             & Coexisting                       \\
					Primary on backscatter & Carrier            & Multiplicative interference & Spreading code           & ---                 & Energy uncertainty               \\
					Backscatter on primary & ---                & Multiplicative interference & Channel uncertainty      & Passive beamforming & Dynamic passive beamforming      \\
					Cooperative devices    & ---                & No                          & Transmitter and receiver & ---                 & Transmitter, nodes, and receiver \\
					Sequential decoding    & ---                & No                          & Primary-to-backscatter   & ---                 & Backscatter-to-primary           \\
					Reflection pattern by  & Information source & Information source          & Information source       & Channel             & Source, channel, and priority    \\
					Input distribution     & Equiprobable       & Equiprobable                & Equiprobable or Gaussian & Degenerate          & Flexible                         \\
					Load-switching speed   & Fast               & Slow                        & Slow                     & Quasi-static        & Arbitrary                        \\ \bottomrule
				\end{tabular}
			}
		\end{table}
		\begin{columns}
			\begin{column}{0.4\textwidth}
				\begin{figure}
					\centering
					\resizebox{\linewidth}{!}{
						\input{../assets/viva/riscatter.tex}
					}
					\label{fg:riscatter}
				\end{figure}
			\end{column}
			\begin{column}{0.5\textwidth}
				\begin{itemize}
						\item {\color{blue}Primary link:} active legacy transmission from an \gls{rf} source
						\item {\color{orange}Backscatter link:} passive free-ride transmission from RIScatter nodes
				\end{itemize}
			\end{column}
		\end{columns}
		RIScatter renders the node input distribution as a function of information source, \gls{csi}, and priority of coexisting links.
	\end{frame}

	\begin{frame}{Signal model}
		\begin{figure}[H]
			\centering
			\def\svgwidth{0.6\columnwidth}
			\input{../assets/viva/riscatter_network.pdf_tex}
			\label{fg:riscatter_network}
		\end{figure}
		Within each backscatter block, received signal at primary block $n$ is
		\begin{equation*}
			y[n] = \underbrace{\mathbf{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} \textcolor{orange}{x_k}}_{\mathbf{h}^\mathsf{H}(\textcolor{orange}{x_{\mathcal{K}}})} \mathbf{w} \textcolor{blue}{s[n]} + v[n],
		\end{equation*}
		\vspace{-0.25cm}
		\begin{block}{Properties}
			\begin{enumerate}
				\item \textcolor{blue}{Primary} and \textcolor{orange}{backscatter} symbols are superimposed by {double modulation}
				\item Backscatter signal is much weaker due to {double fading}
				\item The spreading factor (i.e., symbol period ratio $N$) is usually large
				\item Each {state} is simultaneously part of information and beamforming {codeword}
				\item Reflection pattern over time is guided by input probability distribution
			\end{enumerate}
		\end{block}
	\end{frame}

@@

	\begin{frame}{Joint beamforming, input distribution, and energy detector design}
		\vspace{-0.125cm}
		\begin{block}{Achievable rate}
			\vspace{-0.25cm}
			\begin{align*}
				\sum_k R_{\text{B},k} &= \sum\nolimits_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum\nolimits_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log {P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}/{P(\hat{x}_{m_{\mathcal{K}}'})}\\
				R_{\text{P}} &= \sum\nolimits_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log \left(1 + \frac{\lvert \mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \mathbf{w} \rvert^2}{\sigma_w^2}\right)
			\end{align*}
		\end{block}
		\begin{block}{Problem formulation}
			\vspace{-0.25cm}
			\begin{maxi*}
				{\scriptstyle{\{\mathbf{p}_k\},\mathbf{w},\mathbf{t}}}{\rho R_\text{P} + (1-\rho) \sum\nolimits_{k} R_{\text{B},k}}{}{}
				\addConstraint{\mathbf{1}^\mathsf{T} \mathbf{p}_k=1,}{\quad \mathbf{p}_k \ge \mathbf{0},}{\quad \forall k}
				\addConstraint{t_{l-1} \le t_l,}{\quad t_l \ge 0,}{\quad \forall l}
				\addConstraint{\lVert \mathbf{w} \rVert^2 \le P,}{}{}
			\end{maxi*}
		\end{block}
		\begin{exampleblock}{Solution by \gls{bcd}}
			\begin{itemize}
				\item Input distribution $\{\mathbf{p}_k\}$: \gls{kkt}
				\item Active beamforming $\mathbf{w}$: \gls{pga}
				\item Energy decision threshold $\mathbf{t}$: \gls{dp}
			\end{itemize}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Simulation results: Input distribution}
		\begin{figure}[!t]
			\centering
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/input_distribution.tex}
				}
			}
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/distribution_weights.tex}
				}
			}
		\end{figure}
		\begin{itemize}
			\item \gls{bc} and \gls{ris} are special cases of RIScatter with uniform and degenerate input distribution
			\item Increasing $\rho$ from 0 to 1 creates a smooth transition from backscatter modulation to passive beamforming
		\end{itemize}
	\end{frame}

	\begin{frame}{Simulation results: Rate region}
		\begin{figure}[!t]
			\centering
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/region_comparison.tex}
				}
			}
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/region_duration.tex}
				}
			}
		\end{figure}
		\begin{itemize}
			\item RIScatter backscatter rate is lower than symbiotic radio (due to energy detection) but higher than ambient backscatter (due to adaptive encoding)
			\item A large spreading factor $N$ improves backscatter \glsfmtshort{ber} but reduces data rate
			\item Active and passive transmission can share resource with mutual benefits
		\end{itemize}
	\end{frame}
\end{section}

@@

		\begin{block}{\glsfmtshort{bd}-\glsfmtshort{ris}}
			Each group contains $L$ connected elements, allowing amplitude and phase control
			\vspace{-0.25cm}
			\begin{equation*}
				\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G), \quad \mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}_L, \quad \forall g
				\label{eq:bd_ris}
			\end{equation*}
			\vspace{-0.5cm}
			\begin{itemize}
				\item \emph{Subchannel rearrangement:} allows each group to rearrange and combine the backward and forward subchannels by strength
				\vspace{-0.25cm}
				\begin{equation*}
					\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert \to \sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert
					\vspace{-0.25cm}
				\end{equation*}
				\item \emph{Subspace alignment:} rotate backward-forward (intra-group, multiplicative) and direct-indirect (inter-group, additive) singular vectors
				\vspace{-0.25cm}
				\begin{equation*}
					\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{\Theta}_g \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}
					\label{eq:channel_equivalent_svd}
				\end{equation*}
			\end{itemize}
		\end{block}
	\end{frame}

>>>>

	\begin{frame}{Use cases of \glsfmtshort{ris}}
		\begin{itemize}
			\item \textcolor{blue}{Beamforming} of \gls{ris} and transceiver can be jointly designed for a specific performance measure.
			\item \gls{ris} can be used for backscatter \textcolor{blue}{modulation} by periodically switching the reflection pattern.
			\item \textcolor{blue}{Channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment.
		\end{itemize}

		\begin{figure}
			\centering
			\subfloat[Beamforming \cite{Wu2020}]{
				\resizebox{0.32\textwidth}{!}{
					\includegraphics{../assets/viva/ris_beamforming_swipt.jpg}
				}
			}
			\subfloat[Modulation \cite{Hu2021a}]{
				\resizebox{0.32\textwidth}{!}{
					\includegraphics{../assets/viva/ris_modulation.pdf}
				}
			}
			\subfloat[Channel shaping \cite{Arslan2022}]{
				\resizebox{0.32\textwidth}{!}{
					\includegraphics{../assets/viva/ris_shaping.pdf}
				}
			}
		\end{figure}
	\end{frame}
\end{section}

@@

	\begin{frame}{From received signal to harvested power}
		The rectenna efficiency $\eta_3$ depends on its input waveform (power and shape).
		\begin{block}{Rectenna model}
			\begin{itemize}
				\item Linear region (constant $\eta_3$): $P_{\mathrm{DC}}^\mathrm{R} = \eta_3 P_\mathrm{RF}^\mathrm{R} = \eta_3 \mathbb{A}\bigl\{ \lvert y(t) \rvert^2 \bigr\}$
				\item Non-linear region: Taylor expansion on diode characteristic equation
				\vspace{-0.25cm}
				\begin{equation*}
					\arg_{x(t)} \max P_{\mathrm{DC}}^\mathrm{R} = \arg_{x(t)} \max z \triangleq \sum_{i=2,\text{even}}^{n_0} \beta_i \mathbb{A}\bigl\{ y^i(t) \bigr\},
					\vspace{-0.5cm}
				\end{equation*}
				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant and $n_0$ is the truncation order.
			\end{itemize}
		\end{block}
		\begin{alertblock}{In multi-carrier \glsfmtshort{wpt} \textellipsis}
			\begin{itemize}
				\item $n_0 \ge 4$ allows components to compensate each other for higher \glsfmtshort{dc} power
				\item High \gls{papr} (e.g., multi-sine) is preferred \cite{Trotter2009}
			\end{itemize}
			\vspace{-0.5cm}
			\begin{figure}
				\centering
				\subfloat{
					\resizebox{!}{2.5cm}{
						\includegraphics{../assets/viva/multisine_frequency_domain.eps}
					}
				}
				\subfloat{
					\resizebox{!}{2.5cm}{
						\includegraphics{../assets/viva/multisine_time_domain.eps}
					}
				}
			\end{figure}
		\end{alertblock}
	\end{frame}

	\begin{frame}{From \glsfmtshort{wpt} to \gls{ris}-aided \glsfmtshort{swipt}}
		\begin{figure}[H]
			\centering
			\def\svgwidth{0.3\columnwidth}
			\input{../assets/viva/system.eps_tex}
		\end{figure}

		\begin{itemize}
			\item \gls{swipt} features shared signal, spectrum, and infrastructure
			\item \gls{ris} enhances the RF-to-RF efficiency $\eta_2$ which has been a major concern
		\end{itemize}
		\begin{block}{Transmit waveform}
			\begin{equation*}
				\mathbf{x}(t) = \Re \left\{\sum_{n=1}^N \Bigl(\mathbf{w}_{\mathrm{I},n} \cdot \underbrace{\tilde{x}_{\mathrm{I},n}(t) e^{\jmath 2{\pi}{f_n}{t}}}_\text{modulated}+\mathbf{w}_{\mathrm{P},n} \cdot \underbrace{e^{\jmath 2{\pi}{f_n}{t}}}_\text{multi-sine}\Bigr) \right\}
			\end{equation*}
		\end{block}
		\begin{block}{Receiver architectures}
			\vspace{-0.5cm}
			\begin{figure}
				\centering
				\subfloat[\gls{ts} receiver]{
					\resizebox{0.35\columnwidth}{!}{
						\input{../assets/viva/receiver_ts.tex}
					}
					\label{fg:receiver_ts}
				}
				\subfloat[\gls{ps} receiver]{
					\resizebox{0.35\columnwidth}{!}{
						\input{../assets/viva/receiver_ps.tex}
					}
					\label{fg:receiver_ps}
				}
			\end{figure}
		\end{block}
	\end{frame}

@@

@@

	\begin{frame}{Signal model}
		RIScatter renders the node input distribution as a function of information source, \gls{csi}, and priority of coexisting links.
		\begin{figure}[H]
			\centering
			\def\svgwidth{0.6\columnwidth}
			\input{../assets/viva/riscatter_network.pdf_tex}
			\label{fg:riscatter_network}
		\end{figure}
		\begin{equation*}
			y[n] = \underbrace{\mathbf{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} \textcolor{orange}{x_k}}_{\mathbf{h}^\mathsf{H}(\textcolor{orange}{x_{\mathcal{K}}})} \mathbf{w} \textcolor{blue}{s[n]} + v[n],
		\end{equation*}
		\vspace{-0.25cm}
		\begin{block}{Properties}
			\begin{enumerate}
				\item \textcolor{blue}{Primary} and \textcolor{orange}{backscatter} symbols are superimposed by {double modulation}
				\item Backscatter signal is much weaker due to {double fading}
				\item The spreading factor (i.e., symbol period ratio $N$) is usually large
				\item Each {state} is simultaneously part of information and beamforming {codeword}
				\item Reflection pattern over time is guided by input probability distribution
			\end{enumerate}
		\end{block}
	\end{frame}

@@

	\begin{frame}{Joint beamforming, input distribution, and energy detector design}
		\begin{block}{Problem formulation}
			\vspace{-0.25cm}
			\begin{maxi*}
				{\scriptstyle{\{\mathbf{p}_k\},\mathbf{w},\mathbf{t}}}{\rho R_\text{P} + (1-\rho) \sum\nolimits_{k} R_{\text{B},k}}{}{}
				\addConstraint{\mathbf{1}^\mathsf{T} \mathbf{p}_k=1,}{\quad \mathbf{p}_k \ge \mathbf{0},}{\quad \forall k}
				\addConstraint{t_{l-1} \le t_l,}{\quad t_l \ge 0,}{\quad \forall l}
				\addConstraint{\lVert \mathbf{w} \rVert^2 \le P,}{}{}
			\end{maxi*}
		\end{block}
		\begin{exampleblock}{Solution by \gls{bcd}}
			\begin{itemize}
				\item Input distribution $\{\mathbf{p}_k\}$: \gls{kkt}
				\item Active beamforming $\mathbf{w}$: \gls{pga}
				\item Energy decision threshold $\mathbf{t}$: \gls{dp}
			\end{itemize}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Simulation results: Input distribution and rate region}
		\begin{figure}[!t]
			\centering
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/distribution_weights.tex}
				}
			}
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/region_comparison.tex}
				}
			}
		\end{figure}
		\begin{itemize}
			\item Increasing $\rho$ from 0 to 1 evolves from \gls{bc} to \gls{ris}
			\item Backscatter rate is lower than \glsfmtshort{sr} (due to energy detection) but higher than \glsfmtshort{ambc} (due to adaptive encoding)
			\item Active and passive transmission can share resource with mutual benefits
			% creates a smooth transition from backscatter modulation to passive beamforming
		\end{itemize}
	\end{frame}
\end{section}

@@

		\begin{block}{\glsfmtshort{bd}-\glsfmtshort{ris}}
			Each group contains $L$ connected elements, allowing amplitude and phase control
			% \vspace{-0.25cm}
			\begin{equation*}
				\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G), \quad \mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}_L, \quad \forall g
				\label{eq:bd_ris}
			\end{equation*}
			\vspace{-0.5cm}
			\begin{figure}[H]
				\centering
				\resizebox{0.5\columnwidth}{!}{
					\includegraphics{../assets/viva/bd_ris_architecture_1.eps}
				}
				\caption{Architecture of diagonal and \gls{bd}-\gls{ris} \cite{Shen2020a}}
				\label{fg:bd_ris_architecture_2}
			\end{figure}

		\end{block}
	\end{frame}
